Dynamically Annealed Reinforcement Learning for Intrusion Prevention

### 2017-11-09 paper/paper.tex
[Paper] More initial setup.

%bib
\usepackage[maxnames=3,maxbibnames=99,mincrossrefs=5,backend=bibtex]{biblatex}
%\addbibresource{papers-off.bib}
%\addbibresource{confs-off.bib}
%\addbibresource{rfc.bib}

@@

\usepackage{hyperref}
\usepackage{url}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={Literature + Ideas},
	pdfauthor={Kyle A. Simpson}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

@@

\title{Dynamically Annealed Reinforcement Learning for Intrusion Prevention}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]},\\\emph{University of Glasgow, Glasgow, Scotland},\\
		\email{k.simpson.1@research.gla.ac.uk}}

@@

%% If needed, make urls typewritery
\urlstyle{tt}

@@

>>>>

%bib
\usepackage[maxnames=3,maxbibnames=99,mincrossrefs=5,style=ieee,sortcites,backend=bibtex]{biblatex}
%\addbibresource{papers-off.bib}
%\addbibresource{confs-off.bib}
%\addbibresource{rfc.bib}

@@

\usepackage{hyperref}
\usepackage{url}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={Dynamically Annealed Reinforcement Learning for Intrusion Prevention},
	pdfauthor={Kyle A. Simpson}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

\usepackage{titling}
\settowidth{\thanksmarkwidth}{*}
\setlength{\thanksmargin}{-\thanksmarkwidth}

@@

\title{Dynamically Annealed Reinforcement Learning for Intrusion Prevention}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]},\\\emph{University of Glasgow, Glasgow, Scotland},\\
		\email{k.simpson.1@research.gla.ac.uk}}
\date{}

@@

%% If needed, make urls typewritery
%\urlstyle{tt}

@@

\printbibliography
